Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-04 ms_pre_post.Rmd
Add quantitative statistics to last section of Results

How is evolution of one inbreeding strategy affected by the existence of another already adaptive strategy?
----------------------------------------------

When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A). Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B). However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).

>>>>

How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?
----------------------------------------------

When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A). Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B). However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs. $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).

<!--- Mean pre-cop value is -17.62444  in Figure 1B --->
<!--- Mean pre-cop value is -15.44786  in Figure 4A --->

<!--- I know I've mentioned this too many times, but I'm really not a fan of this kind of quantitative statistic because it doesn't really mean anything in the context of a model like this. At the very least though, I think it's better to put the actual numbers up because ''X% less negative'' just seems very confusing to me. --->
